### 2021-11-09 input/proposal.tex
meow

\begin{algorithm}
  \input{input/algoascast.tex}
  \caption{\label{algo:ascast}\NAME at \Process~$p$ in dynamic networks.}
\end{algorithm}

@@

Algorithm~\ref{algo:ascast} also enables dynamic consistent
partitioning in dynamic networks where \processes can join, leave, or
crash at any time. Removing a \process is equivalent to removing all
its edges, and adding a \process is equivalent to add as many edges as
necessary.  Adding an edge between two \processes may only improve the
shortest path of one of these \processes. Therefore, it triggers a
competition between the two \processes only. If one or the other
\process improves, the propagation of $\alpha$ messages operates
normally.  Removing an edge between two \processes may invalidate the
shortest path of one of involved \processes plus downstream
\processes. As a side effect, removing an edge may also impair the
propagation of a partition delete. To implement this behavior, \NAME
uses its implementation of $\Delta$ messages. This prove costly but
enables \NAME even in dynamic networks subject to physical
partitioning.

>>>>

\begin{algorithm}
  \input{input/algoascast.tex}
  \caption{\label{algo:ascast}\NAME at \Process~$p$.}
\end{algorithm}

@@

\begin{algorithm}
  \input{input/algoedges.tex}
  \caption{\label{algo:edges}\NAME at \Process~$p$ in dynamic networks.}
\end{algorithm}

Algorithm~\ref{algo:edges} enables dynamic consistent partitioning in
dynamic networks where \processes can join, leave, or crash at any
time. Removing a \process is equivalent to removing all its edges, and
adding a \process is equivalent to add as many edges as necessary.
Adding an edge between two \processes may only improve the shortest
path of one of these \processes. Therefore, it triggers a competition
between the two \processes only. If one or the other \process
improves, the propagation of $\alpha$ messages operates normally.
Removing an edge between two \processes may invalidate the shortest
path of one of involved \processes plus downstream \processes. As a
side effect, removing an edge may also impair the propagation of a
partition delete. To implement this behavior, \NAME uses its
implementation of $\Delta$ messages. This prove costly but enables
\NAME even in dynamic networks subject to physical partitioning.
